NTM CT Scoring - Initial Agreement

### 2023-07-29 Stacey Martiniano/ntm_agreement.qmd
started analysis with bronch 0 and 1

```{r}
# Import disease state
outcomes = read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/disease.key.csv",na.strings = "")
outcomes$NTM.PD..Y.N. = factor(outcomes$NTM.PD..Y.N.,
                               levels = c("No","Yes"),ordered = T)
# Remove training scans, get first reading of duplicates, convert to numeric
scores = data %>% 
  filter(scan_id %in% outcomes$cff_registry_id,scorer != "GS") %>%
  group_by(scorer,scan_id) %>%
  slice_min(scoresheet_timestamp) %>% 
  select(scorer, scan_id,bronchiectasis_rul:atelectasis___6) %>%
  mutate(across(contains("bronchiectasis"),
                ~as.numeric(factor(.x,levels=c("Absent","Cylindric",
                                               "Varicose","Cystic"),
                                   labels = c("Unchecked","Checked",
                                              "Checked","Checked")))-1),
         across(mucoid_impaction___1:atelectasis___6,
                ~as.numeric(factor(.x,levels=c("Unchecked","Checked")))-1))
# Take the maximum across all locations
scores = scores %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
               names_to = c("feature", "location"),
               names_pattern = "(.*)_(.*)$"
  ) %>%
  group_by(scorer,scan_id,feature) %>%
  summarise(value = max(value),.groups = "drop") 
# Calculate scores
majority = scores %>%
  group_by(scan_id,feature) %>%
  summarise(value = names(sort(-table(value)))[1],.groups = "drop") %>%
  group_by(scan_id) %>%
  summarise(score = sum(as.numeric(value)))
max = scores %>%
  group_by(scan_id,feature) %>%
  summarise(value = max(value),.groups = "drop") %>%
  group_by(scan_id) %>%
  summarise(score = sum(value))
# Outcomes
majority = left_join(majority,outcomes %>% select(cff_registry_id,NTM.PD..Y.N.),
                   by = join_by(scan_id == cff_registry_id)) %>%
  rename(`NTM-PD` = NTM.PD..Y.N.)
max = left_join(max,outcomes %>% select(cff_registry_id,NTM.PD..Y.N.),
                   by = join_by(scan_id == cff_registry_id)) %>%
  rename(`NTM-PD` = NTM.PD..Y.N.)
```

@@

```{r}
majority %>% select(score,`NTM-PD`) %>%
  tbl_summary(by = `NTM-PD`)
```

>>>>

```{r}
# Import disease state
outcomes = read.csv("/Users/timvigers/Library/CloudStorage/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/Data_Clean/disease.key.csv",na.strings = "")
outcomes$NTM.PD..Y.N. = factor(outcomes$NTM.PD..Y.N.,
                               levels = c("No","Yes"),ordered = T)
# Remove training scans, get first reading of duplicates, convert to numeric
scores = data %>% 
  filter(scan_id %in% outcomes$cff_registry_id,scorer != "GS") %>%
  group_by(scorer,scan_id) %>%
  slice_min(scoresheet_timestamp) %>% 
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6) %>%
  mutate(across(contains("bronchiectasis"),
                ~as.numeric(factor(.x,levels=c("Absent","Cylindric",
                                               "Varicose","Cystic"),
                                   labels = c("Unchecked","Checked",
                                              "Checked","Checked")))-1),
         across(mucoid_impaction___1:atelectasis___6,
                ~as.numeric(factor(.x,levels=c("Unchecked","Checked")))-1))
# Add outcome info
scores = left_join(scores,outcomes %>% select(cff_registry_id,NTM.PD..Y.N.),
                   by = join_by(scan_id == cff_registry_id)) %>%
  rename(`NTM-PD` = NTM.PD..Y.N.)
# Calculate scores
majority = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~tail(names(sort(table(.x))), 1)))
max = scores %>%
  group_by(scan_id) %>%
  summarise(across(bronchiectasis_rul:`NTM-PD`,
                   ~max(.x,na.rm = T)))
a = scores %>%
  filter(scorer == "A")
b = scores %>%
  filter(scorer == "B") 
c = scores %>%
  filter(scorer == "C")
```

```{r}
comp_score = function(df){
  df = df %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
                           names_to = c("feature", "location"),
                           names_pattern = "(.*)_(.*)$"
  ) %>%
    mutate(
      feature = gsub("__", "", feature),
      feature = str_to_title(gsub("_", " ", feature))
    )
  df$location <- factor(df$location,
                        levels = c(
                          "1", "2", "3", "4", "5", "6", "ling", "lll",
                          "lul", "rll", "rml", "rul"
                        ),
                        labels = c(
                          "RUL", "RML", "RLL", "LUL", "Ling", "LLL",
                          "Ling", "LLL", "LUL", "RLL", "RML", "RUL"
                        )
  )
  df$value = as.numeric(df$value)
  # Tables
  # Total score
  sums = df %>% group_by(scan_id,`NTM-PD`) %>%
    summarise(Total = sum(value),.groups = "drop") 
  t1 = tableby(`NTM-PD`~Total,data = sums,numeric.test = "kwt",
               numeric.stats = c("Nmiss2","median","q1q3","range"))
  # By feature
  sums = df %>% group_by(scan_id,`NTM-PD`,feature) %>%
    summarise(score = sum(value),.groups = "drop") %>%
    pivot_wider(names_from = feature,values_from = score)
  f = as.formula(paste0("`NTM-PD`~",paste0(paste0("`",unique(df$feature),"`"),
                                           collapse = "+")))
  t2 = tableby(f,data = sums,numeric.test = "kwt",
               numeric.stats = c("Nmiss2","median","q1q3","range"))
  # By location
  sums = df %>% group_by(scan_id,`NTM-PD`,location) %>%
    summarise(score = sum(value),.groups = "drop") %>%
    pivot_wider(names_from = location,values_from = score)
  f = as.formula(paste0("`NTM-PD`~",paste0(paste0("`",unique(df$location),"`"),
                                           collapse = "+")))
  t3 = tableby(f,data = sums,numeric.test = "kwt",
               numeric.stats = c("Nmiss2","median","q1q3","range"))
  # Plots
  total_plot = df %>% group_by(scan_id,`NTM-PD`,feature) %>%
    summarise(score = sum(value),.groups = "drop") %>%
    ggplot(.,aes(x = `NTM-PD`, y = score,fill = `NTM-PD`)) + 
    geom_violin() +
    theme_bw() + 
    theme(legend.position = "none")
  feature_plot = total_plot +
    facet_wrap(~feature,scales = "free") 
  location_plot = df %>% group_by(scan_id,`NTM-PD`,location) %>%
    summarise(score = sum(value),.groups = "drop") %>%
    ggplot(.,aes(x = `NTM-PD`, y = score,fill = `NTM-PD`)) + 
    geom_violin() +
    theme_bw() + 
    theme(legend.position = "none") +
    facet_wrap(~location,scales = "free") 
  # Print
  cat("\n")
  cat("### Total Scores")
  cat("\n")
  cat("\n")
  print(summary(t1,pfootnote = T))
  cat("\n")
  cat("\n")
  print(total_plot)
  cat("\n")
  cat("\n")
  cat("### Scores by Feature")
  cat("\n")
  cat("\n")
  print(summary(t2,pfootnote = T))
  cat("\n")
  cat("\n")
  print(feature_plot)
  cat("\n")
  cat("\n")
  cat("### Scores by Location")
  cat("\n")
  cat("\n")
  print(summary(t3,pfootnote = T))
  cat("\n")
  cat("\n")
  print(location_plot)
  cat("\n")
  cat("\n")
}
```

@@

```{r results='asis'}
comp_score(majority)
```
